Pre-processing Data from Questions Context-less Corpus Study

### 2021-11-11 analysis/exploratory/all_nocontext/rscripts/pre-processing.Rmd
added initial files from old repo

---
title: "Pre-processing Data from Embedded Questions Corpus Study"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")
```

# Read in data
```{r import data}
# Read database
corp = read.table("../../../corpus/results/swbd.tab",sep="\t",header=T,quote="")
# Read experimental data in
d = read.csv("../data/exp04_main-merged.csv")
nrow(d) # 174549
```

## Combine with database
```{r combine raw data with corpus file}
# rename item_id from corpus file
names(corp)[names(corp) == "Item_ID"] <- "tgrep_id"

@@

# join dfs together
d <- left_join(d, corp_match, by="tgrep_id")
# assign the negative values 0
d$rating[d$rating < 0] = 0
nrow(d) # 174549
```

```{r take a look at the raw distribution, include = FALSE}
ggplot(d, aes(x=rating)) +
  geom_histogram()

summary(d) # this doesn't show any negative rating values....
tail(d)
```

# Native speakers
## We exclude any speakers who did not report English as a native language in the post-survey demographic questions.
```{r Filter out non-native English speakers, warning = FALSE}
nrow(d) # 174549
length(unique(d$workerid)) # 1073
#filter out participants who did not report English as native language
d <- d %>%
  mutate(language = tolower(subject_information.language)) %>%
  filter(., grepl("eng", language))

# 25 participants removed for reporting non-english native language
nrow(d) #170068
length(unique(d$workerid)) # 1048
```

@@

## Graph control trials
```{r, eval=FALSE, include=FALSE}
agr = c %>%
  group_by(EntireSentence,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge") +
  facet_wrap(~EntireSentence, labeller = labeller(Sentence = label_wrap_gen(1)))
# ggsave("../graphs/main_controls.pdf")
```

# Remove subjects who failed 2/6 controls
```{r}
# for each control trial type, create a binary measure of whether the
# trial was passed
t = c %>%
  separate(tgrep_id,into=c("tgrep_id","para","trial"),sep="[_]") %>%
  group_by(workerid,paraphrase,trial) %>%
  filter(trial %in% c("movie", "book"), paraphrase %in% c("the")) %>%
  mutate(control_passed = ifelse(rating > .5,"1","0"))
# nrow(t) #2028
a1 = c %>%
  separate(tgrep_id,into=c("tgrep_id","para","trial"),sep="_") %>%
  group_by(workerid,paraphrase,trial) %>%
  filter(trial %in% c("novels", "cookies"), paraphrase %in% c("all")) %>%
  mutate(control_passed = ifelse(rating > .5,"1","0"))
# nrow(a1) #2028
a2 = c %>%
  separate(tgrep_id,into=c("tgrep_id","para","trial"),sep="_") %>%
  group_by(workerid,paraphrase,trial) %>% 
  filter(trial %in% c("tissue", "napkin"), paraphrase %in% c("a")) %>%
  mutate(control_passed = ifelse(rating > .5,"1","0"))
# nrow(a2) #2028

@@

# How many removed using this criterion
length(unique(failed_controls$workerid)) # 37
length(unique(failed_controls$workerid))/length(unique(d$workerid))*100 # 3.5%

```
# Look at raw test items
```{r}
test = d %>%
  # Remove participants who fail 2/6 controls
  filter(!workerid %in% c(failed_controls$workerid)) %>%
  # Remove non-test items
  filter(!tgrep_id %in% c("example1", "example2", "example3", "example4","bot_check")) %>%
  filter(!grepl("control",tgrep_id)) %>%
  # Make a single matrix verb column
  unite("MatrixVerb", c("MatrixPredVerb", "MatrixPredOther", "MatrixPredParticle"), na.rm = TRUE, sep = " ", remove = FALSE) %>%
  # Remove leading and trailing whitespace
  mutate(MatrixVerb = str_trim(MatrixVerb))

@@

# Assign 0 to NaN
test[is.na(test)] <- 0
nrow(test) # 113632
```

## Recoding 
* 15 cases where MatrixVerbs weren't printed with TDTLite
* Modals
* QuestionType
```{r}
# 61188:30 --> funny 
test$MatrixVerb[test$tgrep_id == "61188:30"] = "funny"
test$VerbLemma[test$tgrep_id == "61188:30"] = "funny"
test$MatrixPredVerb[test$tgrep_id == "61188:30"] = "funny"

@@

test[is.na(test$EmbeddedSQ)] <- "no"
test$QuestionType = as.factor(test$QuestionType)

test$EmbeddedSQ = as.character(test$EmbeddedSQ)
test$QuestionType = as.character(test$QuestionType)
test$QuestionType[test$EmbeddedSQ == "yes"] <- "embeddedSAI"
test$EmbeddedSQ = as.factor(test$EmbeddedSQ)
test$QuestionType = as.factor(test$QuestionType)

table(test$QuestionType)
length(unique(test$workerid))
length(unique(test$workerid[test$QuestionType!="embeddedSAI"])) 
```

## Graph raw test items
```{r, eval=FALSE, include=FALSE}
agr = test %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/test_everything.pdf")

length(unique(test$MatrixVerb)) # 175 verbs

@@

## Remove rhetorical questions
```{r}
test_agr = test %>%
  group_by(tgrep_id, paraphrase) %>%
  summarize(mean_rating = mean(rating))

other_ratings = test %>%
  group_by(tgrep_id, Sentence, paraphrase) %>%
  summarize(mean_rating = mean(rating)) %>%
  filter((mean_rating[paraphrase == "other"] > mean_rating[paraphrase=="a"]) & 
           (mean_rating[paraphrase == "other"] > mean_rating[paraphrase=="every"]) & 
           (mean_rating[paraphrase == "other"] > mean_rating[paraphrase=="the"]))

View(other_ratings)

# How much data removed
nrow(other_ratings)/nrow(test_agr)*100 # 15.5%
nrow(test_agr) # 4052

or_ids = other_ratings$tgrep_id
test_other = test %>%
  filter(tgrep_id %in% or_ids)
nrow(test_other)/nrow(test)*100 # 15.5

test_other %>%
  filter(paraphrase == "other") %>%
  group_by(Sentence, paraphrase) %>%
  summarize(mean_rating = mean(rating))  # %>%
  View()

@@

nrow(test_norm)/nrow(test)*100 # 84%

nrow(test_norm) # 95956

# write.csv(test_norm,"../data/embedded_no_rhetorical.csv")
```

# Looing at QuestionType
## Look at SAI and Particle Verbs in Rhetorical Qs
```{r, include = FALSE}
length(unique(test_other$Sentence)) # 159 items

@@

## Look at SAI and Particle Verbs in Test Qs
```{r, include = FALSE}
# In the test data, look at embedded SAI
sq = test_norm %>%
  filter(EmbeddedSQ == "yes")

@@

## Look at questions in test data without embedded SAI

```{r, include = FALSE}
# In the test data questions without embedded SAI
no_sq = test_norm %>%
  filter(EmbeddedSQ != "yes")

@@

## Graph Embedded Subject-Aux Inversion
```{r, include = FALSE}
agr = test_norm %>%
  group_by(EmbeddedSQ,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

# Look at Matrix Verbs
```{r, eval=FALSE, include=FALSE}
verb_count = test %>%
  group_by(VerbLemma) %>%
  summarize(count = n())
View(verb_count)

@@

# Focusing just on "Every", "a" and "the"
## Normalize ratings to make a probability distribution

```{r }
# remove 'other' ratings
# critical with embeddedSQ = 71967
# critical withOUT embeddedSQ = 66963
critical = test_norm %>%
  filter(paraphrase %in% c("every","a","the"))
  # filter((MatrixPredParticle == "") & (EmbeddedSQ != "yes"))
# nrow(critical)
# View(critical)
# unique by-item/by-participant combo
critical$ids = paste(critical$workerid,critical$tgrep_id)

@@

nrow(normed) # 64911
names(normed)

# subset the data to just the relevant columns so that we don't encounter \
# a large file storage problem on GitHub
normed <- normed[,c("workerid","tgrep_id","Sentence","paraphrase","ModalPresent","normed_rating","QuestionType","Finite","Modal","Wh","VerbLemma")]

# save to .csv to load into analysis script
# write.csv(normed,"../data/normed.csv")

## Graph normed data Overall
```{r}
agr = normed %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

dodge = position_dodge(.9)
ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  ylim(0,.6) +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/overall_noSQ.pdf",width=2,height=2)
```

## Graph Interaction between Modal and Wh
```{r}

@@

# ggsave("../graphs/modxwh_noSQ.pdf",width=3,height=4)
```

## Look at just Wh
```{r}
agr = normed %>%
  group_by(paraphrase,Wh) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()
# Re-Order the WH-levels by overall composition of DB
agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))
ggplot(agr,aes(x=Wh, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9))  +
  # ggtitle("Mean rating for Wh-Word") +
  xlab("Wh-Word") +
  ylab("Mean rating") +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/final_normed_wh.pdf")
```

## Look at just ModalPresent
```{r}
agr = normed %>%
  group_by(paraphrase,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

# Graph individual verbs
```{r }
agr = normed %>%
  filter(VerbLemma == "know") %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

ex = test %>%
  filter(tgrep_id == "39551:19")
View(ex[,c("SentenceParse")])
```
(TOP (S (CC and) 
        (NP-SBJ-2 (PRP I)) 
        (VP (VBP have) 
            (VP (VBN been) 
                (VP (VBG debating) (SBAR (WHNP-1 (WP what)) (S (NP-SBJ (-NONE- *-2)) (VP (TO to) (VP (VB cook) (NP (-NONE- *T*-1)))))) (SBAR-PRP (IN because) (S (NP-SBJ (NP (CD one)) (PP (IN of) (NP (PRP$ my) (NNS guests)))) (VP (VBZ is) (NP-PRD (DT a) (NN vegetarian)))))))) (. .) (-DFL- E_S)))

>>>>

---
title: "Pre-processing Data from Questions Context-less Corpus Study"
author: Morgan Moyer
date: May 18, 2021
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")
```

```{r import data}
# Read database
corp = read.table("../../../../corpus/results/swbd.tab",sep="\t",header=T,quote="")
# Read experimental data in
d = read.csv("../data/exp0506-merged.csv")
```

```{r combine raw data with corpus file,warning=FALSE}
# rename item_id from corpus file
names(corp)[names(corp) == "Item_ID"] <- "tgrep_id"

@@

# join dfs together
d <- left_join(d, corp_match, by="tgrep_id")
# assign the negative values 0
d$rating[d$rating < 0] = 0
# table(d$proliferate.condition)

root = d %>%
  filter(grepl("experiment_05",proliferate.condition))
root$QuestionType <- "root"
emb = d %>%
  filter(grepl("experiment_06",proliferate.condition))
emb$QuestionType <- "embedded"
emb$QuestionType[emb$EmbeddedSQ=="yes"] <- "embeddedSAI"
# test[is.na(test$EmbeddedSQ)] <- "no"

d <- full_join(root,emb)

table(d$QuestionType)
```

```{r take a look at the raw distribution, include=FALSE, echo=FALSE}
ggplot(d, aes(x=rating)) +
  geom_histogram()

rq = d %>%
  filter(QuestionType == "root")

length(unique(rq$tgrep_id)) # 847
names(rq)
table(rq$proliferate.condition)

# Native speakers
## We exclude any speakers who did not report English as a native language in the post-survey demographic questions.
```{r Filter out non-native English speakers, warning = FALSE}
nrow(d) # 215028
length(unique(d$workerid)) # 1373
#filter out participants who did not report English as native language
d <- d %>%
  mutate(language = tolower(subject_information.language)) %>%
  filter(., grepl("eng", language))

# 56 participants removed for reporting non-English native language
nrow(d) #206191
length(unique(d$workerid)) # 1317
```

@@

```{r Graph control trials, eval=FALSE, include=FALSE}
agr = c %>%
  group_by(EntireSentence,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge") +
  facet_wrap(~EntireSentence, labeller = labeller(Sentence = label_wrap_gen(1)))
ggsave("../graphs/main_controls.pdf")
```

# Remove Subjects who failed 2/6 Controls
```{r Remove subjects who failed 2/6 controls}
# for each control trial type, create a binary measure of whether the
# trial was passed
t = c %>%
  separate(tgrep_id,into=c("tgrep_id","para","trial"),sep="[_]") %>%
  group_by(workerid,paraphrase,trial) %>%
  filter(trial %in% c("movie", "book"), paraphrase %in% c("the")) %>%
  mutate(control_passed = ifelse(rating > .5,"1","0"))
# nrow(t) #2028
a1 = c %>%
  separate(tgrep_id,into=c("tgrep_id","para","trial"),sep="_") %>%
  group_by(workerid,paraphrase,trial) %>%
  filter(trial %in% c("novels", "cookies"), paraphrase %in% c("all")) %>%
  mutate(control_passed = ifelse(rating > .5,"1","0"))
# nrow(a1) #2028
a2 = c %>%
  separate(tgrep_id,into=c("tgrep_id","para","trial"),sep="_") %>%
  group_by(workerid,paraphrase,trial) %>% 
  filter(trial %in% c("tissue", "napkin"), paraphrase %in% c("a")) %>%
  mutate(control_passed = ifelse(rating > .5,"1","0"))
# nrow(a2) #2028

@@

# How many removed using this criterion
length(unique(failed_controls$workerid)) # 94
length(unique(failed_controls$workerid))/length(unique(d$workerid))*100 # 7.13%

# Look at raw test items

```{r Look at raw test items}
test = d %>%
  # Remove participants who fail 2/6 controls
  filter(!workerid %in% c(failed_controls$workerid)) %>%
  # Remove non-test items
  filter(!tgrep_id %in% c("example1", "example2", "example3", "example4","bot_check")) %>%
  filter(!grepl("control",tgrep_id)) %>%
  # Make a single matrix verb column
  unite("MatrixVerb", c("MatrixPredVerb", "MatrixPredOther", "MatrixPredParticle"), na.rm = TRUE, sep = " ", remove = FALSE) %>%
  # Remove leading and trailing whitespace
  mutate(MatrixVerb = str_trim(MatrixVerb))

@@

# Assign 0 to NaN
test[is.na(test)] <- 0
# nrow(test) # 141816
```

## Recode 
* 15 cases where MatrixVerbs weren't printed with TDTLite
* Modals
```{r, Recode}
# 61188:30 --> funny 
test$MatrixVerb[test$tgrep_id == "61188:30"] = "funny"
test$VerbLemma[test$tgrep_id == "61188:30"] = "funny"
test$MatrixPredVerb[test$tgrep_id == "61188:30"] = "funny"

@@

table(test$QuestionType)
```

# Graph Raw test items
```{r Graph raw test items, eval=FALSE, include=FALSE}
agr = test %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/test_everything.pdf")

length(unique(test$MatrixVerb)) # 193 verbs

@@

# Remove Rhetorical Questions

```{r Remove rhetorical questions}
test_agr = test %>%
  group_by(tgrep_id, paraphrase) %>%
  summarize(mean_rating = mean(rating))

other_ratings = test %>%
  group_by(tgrep_id, paraphrase) %>%
  summarize(mean_rating = mean(rating)) %>%
  filter((mean_rating[paraphrase == "other"] > mean_rating[paraphrase=="a"]) & 
           (mean_rating[paraphrase == "other"] > mean_rating[paraphrase=="every"]) & 
           (mean_rating[paraphrase == "other"] > mean_rating[paraphrase=="the"]))

# How much data removed
nrow(other_ratings)/nrow(test_agr)*100 # 17%
nrow(test_agr) # 8032

or_ids = other_ratings$tgrep_id
test_other = test %>%
  filter(tgrep_id %in% or_ids)
nrow(test_other)/nrow(test)*100 # 17

@@

nrow(test_norm)/nrow(test)*100 # 82%

# write.csv(test_norm,"../data/no_rhetorical.csv")
```

# embedded SAI
```{r Look at SAI and Particle Verbs in Rhetorical Qs, include = FALSE}
length(unique(test_other$Sentence)) # 159 items

@@

```{r, Look at SAI and Particle Verbs in Test Qs, include = FALSE}
# In the test data, look at embedded SAI
sq = test_norm %>%
  filter(EmbeddedSQ == "yes")

@@

```{r, Look at questions in test data without embedded SAI, include = FALSE}
# In the test data questions without embedded SAI
no_sq = test_norm %>%
  filter(EmbeddedSQ != "yes")

@@

## Graphs
```{r Graph Embedded Subject-Aux Inversion, include = FALSE}
agr = test_norm %>%
  group_by(EmbeddedSQ,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

```{r Look at Matrix Verbs, eval=FALSE, include=FALSE}
verb_count = test %>%
  group_by(VerbLemma) %>%
  summarize(count = n())
View(verb_count)

@@

# Normalize ratings

```{r Normalize ratings to make a probability distribution}
# remove 'other' ratings
# critical with embeddedSQ = 71967
# critical withOUT embeddedSQ = 66963
critical = test_norm %>%
  filter(paraphrase %in% c("every","a","the"))
  # filter((MatrixPredParticle == "") & (EmbeddedSQ != "yes"))
# nrow(critical)
# View(critical)
# unique by-item/by-participant combo
critical$ids = paste(critical$workerid,critical$tgrep_id)

@@

# save to .csv to load into analysis script
# write.csv(normed,"../data/normed.csv")
```

# Graph normed data

## Overall

```{r Graph normed data Overall}
agr = normed %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

dodge = position_dodge(.9)
ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  ylim(0,.6) +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/overall.pdf",width=2,height=2)
```

## QuestionType
```{r}
agr = normed %>%
  group_by(QuestionType,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=QuestionType, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  # facet_grid(EmbeddedSQ~Wh) +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  # guides(alpha=guide_legend(title="Embedded SAI")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/overall_QT.pdf",width=3,height=3)
```
## Modal x Wh-Word

```{r Look at Interaction between Modal and Wh}

@@

# ggsave("../graphs/modxwh.pdf",width=3,height=4)
```

```{r Look at just Wh}
agr = normed %>%
  group_by(paraphrase,Wh) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()
# Re-Order the WH-levels by overall composition of DB
agr$Wh <- factor(agr$Wh, levels=c("what","how","where","why","who","when"))
ggplot(agr,aes(x=Wh, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9))  +
  # ggtitle("Mean rating for Wh-Word") +
  xlab("Wh-Word") +
  ylab("Mean rating") +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/final_normed_wh.pdf")
```

```{r Look at just ModalPresent}
agr = normed %>%
  group_by(paraphrase,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

```{r Look at individual verbs}
agr = normed %>%
  filter(VerbLemma == "know") %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

ex = test %>%
  filter(tgrep_id == "39551:19")
